04_LDA_v2

### 2019-12-23 analysis/04_LDA.Rmd
faceted figrues

plotfacetresults2 <- function(df, whichgroups, mysubstitle, myshape){
  p <- df %>%
    filter(treatment %in% whichgroups) %>%
  ggplot(aes(x = treatment, fill = predictedstage)) +
  geom_bar(position = position_fill(reverse = F))  +
  facet_wrap(~sex) +
    theme_B3() +
  theme(legend.position = "none") +
  scale_fill_manual(values = colorscharmaip) +
  labs(y = mysubstitle) 
  return(p)
}

>>>>

plotfacetresults2 <- function(df, whichgroups, mysubstitle, myshape){
  p <- df %>%
    filter(treatment %in% whichgroups) %>%
  ggplot(aes(x = treatment, fill = predictedstage)) +
  geom_bar(position = position_fill(reverse = F))  +
  facet_wrap(~sex) +
    theme_B3() +
  theme(legend.position = "none") +
  scale_fill_manual(values = colorscharmaip) +
  labs(y = mysubstitle)  +
    geom_hline(yintercept = 0.5,  size = 0.25, linetype = 2)
  return(p)
}

### 2019-12-23 analysis/04_LDA_v2.Rmd
faceted figrues

plotpredictions <- function(df, mysubstitle){
  ggplot(df, aes(x = treatment, fill = predictedstage)) +
  geom_bar(position = position_fill(reverse = F))  +
  facet_wrap(~sex) +
    theme_B3() +
  theme(legend.position = "none",
        axis.text.x = element_blank()) +
  scale_fill_manual(values = colorsnewgrouping) +
  labs(y = mysubstitle) 
}

a <- plotpredictions(LDA.hyp, "hypothalamus") + theme(legend.position = "top") 
b <- plotpredictions(LDA.pit, "pituitary") + theme(strip.text = element_blank())
c <- plotpredictions(LDA.gon, "gonads") + theme(axis.text.x = element_text(angle = 45, hjust = 1), strip.text = element_blank())

plot_grid(a,b,c, rel_heights = c(1.8,1,1.5), nrow = 3)

>>>>

plotpredictions <- function(df, whichlevels, mysubstitle){

  p <- df %>%
    filter(treatment %in% whichlevels)  %>%
  ggplot(aes(x = treatment, fill = predictedstage)) +
  geom_bar(position = position_fill(reverse = F))  +
  facet_wrap(~sex) +
    theme_B3() +
  theme(legend.position = "none",
        axis.text.x = element_blank()) +
  scale_fill_manual(values = colorsnewgrouping) +
  labs(y = mysubstitle, x = NULL) +
    geom_hline(yintercept = 0.5,  size = 0.25, linetype = 2)
  return(p)
}

a <- plotpredictions(LDA.hyp, alllevels, "hypothalamus") + theme(legend.position = "top") 
b <- plotpredictions(LDA.pit, alllevels,"pituitary") + theme(strip.text = element_blank())
c <- plotpredictions(LDA.gon, alllevels, "gonads") + theme(axis.text.x = element_text(angle = 45, hjust = 1), strip.text = element_blank())

plot_grid(a,b,c, rel_heights = c(1.6,1,1.2), nrow = 3)

a <- plotpredictions(LDA.hyp, levelstiming, "hypothalamus") + theme(legend.position = "top") 
b <- plotpredictions(LDA.pit, levelstiming,"pituitary") + theme(strip.text = element_blank())
c <- plotpredictions(LDA.gon, levelstiming, "gonads") + theme(axis.text.x = element_text(angle = 45, hjust = 1), strip.text = element_blank())

plot_grid(a,b,c, rel_heights = c(1.6,1,1.2), nrow = 3)

a <- plotpredictions(LDA.hyp, levelsremoval, "hypothalamus") + theme(legend.position = "top") 
b <- plotpredictions(LDA.pit, levelsremoval,"pituitary") + theme(strip.text = element_blank())
c <- plotpredictions(LDA.gon, levelsremoval, "gonads") + theme(axis.text.x = element_text(angle = 45, hjust = 1), strip.text = element_blank())

plot_grid(a,b,c, rel_heights = c(1.6,1,1.2), nrow = 3)
